Kids Combination

### 2019-08-28 stats/kids_basic_me.Rmd
fix reference to datafiles

```{r}
# import data
d <- read_csv("../data/child_basic_me.csv")%>%
  mutate(subage = factor(subage))

@@

model_plot <- ggplot(ranef_plot, aes(x=age,y = y, col = familiar))+
  geom_hline(yintercept = 0.5, lty=2)+
  geom_line(size = 1)+
  ggtitle("Model")+
  labs(x="Age",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_viridis_d(name = "familiar object")

>>>>

```{r}
# import data
d <- read_csv("../data/me.csv")%>%
  mutate(subage = factor(subage))

@@

model_plot <- ggplot(ranef_plot, aes(x=age,y = y, col = familiar))+
  geom_hline(yintercept = 0.5, lty=2)+
  geom_line(size = 1)+
  ggtitle("Model")+
  labs(x="Age",y="Mutual Exclusivity effect")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_viridis_d(name = "familiar object")

### 2019-08-28 stats/kids_combination.Rmd
fix reference to datafiles

```{r}
d %>%
  filter(condition != "train")%>%
  group_by(condition,subage) %>%
  summarise(n = length(unique(subid)),
            data_points = n())
```

@@

model <- brm(correct ~ familiarObject * age_num * condition,
                    data = d_model, family = bernoulli(),
          control = list(adapt_delta = 0.95),
          sample_prior = F,
          save_all_pars = TRUE,
          iter = 5000)

@@

plot(model)

>>>>

```{r}
d %>%
  filter(condition != "train")%>%
  group_by(condition,subage) %>%
  summarise(n = length(unique(subid)),
            data_points = n())

#length(unique(d$subid))
```

@@

model <- brm(correct ~ familiarObject * age_num * condition + (condition|subid),
                    data = d_model, family = bernoulli(),
          control = list(adapt_delta = 0.99),
          sample_prior = F,
          save_all_pars = TRUE,
          iter = 8000)

@@
